WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-08 method/sec_0_introduction.tex
v5.1.1
Make geo- consistent

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Modules of a Weather Data System}
\label{subse:modules_weather_data_integration_sys}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=1\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Modules of a weather data system.}
\label{fi:wdia_components}
\end{figure}

\subsubsection{Integration }
The system should be capable of integrating data from different sources such as satellite data, high end, and low-end weather station. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also, those models reproduce a large set of redundant data. Thus, the system should store the bulk data while optimizing the disk space.
\subsubsection{Dissemination}
Then different users should be able to retrieve data as they require. Also, the users should be able to easily search into the available information in the system based on timeseries metadata or based on Geo queries.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Modules of a Weather Data System}
% \label{subse:modules_weather_data_integration_sys}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=1\textwidth]{method/misc/weather_data_system_components.pdf}}
\caption{Modules of a weather data system.}
\label{fi:wdia_components}
\end{figure}

\subsubsection{Integration }
The system should be capable of integrating data from different sources such as satellite data, high end, and low-end weather station. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also, those models reproduce a large set of redundant data. Thus, the system should store the bulk data while optimizing the disk space.
\subsubsection{Dissemination}
Then different users should be able to retrieve data as they require. Also, the users should be able to easily search into the available information in the system based on timeseries metadata or based on geo-queries.

### 2020-05-08 method/sec_4-db_struct.tex
Make geo- consistent

To provide fast geo-search queries, we have to use a database system that supports geo indexing. We used MongoDB, which is a document-oriented database with Geo indexing capabilities. Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports:

@@

We used MongoDB geospatial features to support Geo queries in the \acrshort{wdias}. Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries. If particular timeseries metadata not present in the adapter-query, then fetch metadata from the adapter-metadata and indexed in the MongoDB. Vise a versa; when a new timeseries created in the adapter-metadata, it triggers an event to index metadata in the adapter-query.
Here we used the \emph{y-axis scaling} concept by splitting metadata search into multiple services. Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.

>>>>

To provide fast geo-search queries, we have to use a database system that supports geo indexing. We used MongoDB, which is a document-oriented database with geo indexing capabilities. Also, MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database, and supports:

@@

We used MongoDB geospatial features to support geo-queries in the \acrshort{wdias}. Also, we indexed the timeseries metadata with other indexing features to serve external timeseries metadata queries. If particular timeseries metadata not present in the adapter-query, then fetch metadata from the adapter-metadata and indexed in the MongoDB. Vise a versa; when a new timeseries created in the adapter-metadata, it triggers an event to index metadata in the adapter-query.
Here we used the \emph{y-axis scaling} concept by splitting metadata search into multiple services. Within the system, it uses in-memory database cache to support internal metadata access, and external search queries fulfill by the adapter-query with using MongoDB.

### 2020-05-08 method/sec_6-query.tex
Make geo- consistent

We used the adapter-query primarily for supporting Geo-spatial queries. As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well. The Appendix B described the search query capabilities of \acrshort{wdias}.
The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
Also, it provides a set of Geo query endpoints, and users can perform Geo search queries with sending geo-information in geoJson format. The following Geo queries are supported by the system, and a detailed description appears in Appendix B.
\begin{itemize}
    \item Query Locations within Area
    \item Query parameters in Locations
    \item Query Timeseries by Location
    \item Query Timeseries by Locations
    \item Query Timeseries by Parameter
    \item Query Timeseries in Area
    \item Query Timeseries in Area by Parameter
    \item Query All Timeseries
\end{itemize}

>>>>

We used the adapter-query primarily for supporting geo-spatial queries. As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well. The Appendix B described the search query capabilities of \acrshort{wdias}.
The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
Also, it provides a set of geo-query endpoints, and users can perform geo-search queries with sending geo-information in geoJson format. The following geo-queries are supported by the system, and a detailed description appears in Appendix B.
\begin{itemize}
    \item Query Locations within Area
    \item Query parameters in Locations
    \item Query Timeseries by Location
    \item Query Timeseries by Locations
    \item Query Timeseries by Parameter
    \item Query Timeseries in Area
    \item Query Timeseries in Area by Parameter
    \item Query All Timeseries
\end{itemize}

### 2020-05-08 method/sec_7-summary.tex
Make geo- consistent

Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support Geo search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

>>>>

Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support geo-search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

### 2020-05-08 results/sec_1-test_plan.tex
Make geo- consistent

Other than the above modules, \emph{adapter modules} act as the core modules and the base of the system. Also, the \emph{query module} allows the users to query for the timeseries based on the metadata and perform Geo-based queries based on the locations.

>>>>

Other than the above modules, \emph{adapter modules} act as the core modules and the base of the system. Also, the \emph{query module} allows the users to query for the timeseries based on the metadata and perform geo-based queries based on the locations.
